SunPy - Python for Solar Physics

### 2014-01-29 5-Dev.tex
Cadair passes the ball
dropped the 'Development workflow section, retaining the salient points about the SunPy community and dropping the git/github description.

The continued success of an open-source project depends on many factors;
three of the most important are (1) utility and quality of the code, (2) documentation, and (3) an
active community \citep{bangerth2013}. Several tools (some specific to Python) are used by
SunPy to make achieving these goals more accessible. To maintain high-quality code, a 
transparent and collaborative development workflow made possible by GitHub is used (described
further below).
Additionally, SunPy makes use of `continuous integration' provided by
\href{http://travis-ci.org}{Travis CI}, a process by which the addition of any new code 
automatically triggers a comprehensive review of written unit tests. If any single test
fails then the community is alerted before the code is accepted. The unit test coverage is
also monitored by the \href{http://coveralls.io}{Coveralls} service.

Quality documentation is
one of the most important factors determining the success of any software project. 
Thankfully powerful tools already exist in Python to support this thanks to native
Python's focus on its own documentation. SunPy makes use of the \href{http://sphinx-doc.org}{Sphinx}
documentation generator. Sphinx uses reStructuredText as its markup language: 
an easy-to-read, what-you-see-is-what-you-get plaintext markup syntax. It supports
many output formats most notably HTML as well as PDF, and ePub and provides a rich
hierarchically structured view of in-code documentation strings. The SunPy documentation 
is built automatically and is hosted by \href{http://readthedocs.org}{Read the 
Docs} at \url{http://docs.sunpy.org}.

In order to maintain an active community, communication is key.  The SunPy community makes
use of a number of channels to communicate. For immediate communications, an active IRC chat
room (\#SunPy) is hosted on freenode.net. For more involved or less immediate needs, such as
developer comments or discussions, a open mailing list is hosted on Google Groups. 
Discussion of bugs and bug tracking are provided directly on GitHub as well as new
code-review discussions.
% RJH: do we want to list both the community and dev lists?

% RJH: This section is redundant with some parts in the text.  I favor cutting the stuff in text.
% schriste - we had agreed to only refer to the support in one place. we need to agree as to where
Many of the larger features in SunPy have been developed 
with the support of both the ESA-SOCIS and GSOC. 
Initial development of SunPy's VSO and HEK 
implementations were funded by the SOCIS program as well as a prototyped GUI 
and N-Dimensional datatype implementations. SunPy was supported by GSOC in 2013 
through the \href{http://www.python.org/psf/}{Python Software Foundation} (PSF). It supported development of the 
\texttt{HELIO} and 
\texttt{database} subpackages.

\subsection{Development Workflow}
The development workflow that GitHub enables is simple and transparent. The 
primary source code repository \url{http://github.com/sunpy/sunpy} can be 
`forked' by anyone with a GitHub account who can then modify their fork as they 
wish. Upon completion of any modifications it is possible for a user to create 
a `Pull Request' (\url{http://github.com/sunpy/sunpy/pulls}) to the main SunPy 
repository in order to incorporate their modification into the SunPy code base. 
Pull requests are reviewed by the SunPy community before being accepted. Community consensus
is required to add new features.

Pull requests are a very powerful tool to maintain code quality, as each line 
of code that has been modified is highlighted for review and can be commented on. 
In order to maintain high quality code the following conditions must typically be met 
before code is accepted.

\begin{enumerate}
	\item  The code must follow 	
	\href{http://www.python.org/dev/peps/pep-0008/}{PEP8} the Python style 
	guidelines, this keeps all the code in SunPy styled in a consistent manner and easy to read.

@@

	\item The code must contain significant unit test coverage.
\end{enumerate}

This kind of development model is widely used within the scientific Python 
community as well as by a wide variety of other projects both open and closed 
source.

>>>>

The continued success of an open-source project depends on many factors;
three of the most important are (1) utility and quality of the code, (2) documentation, and (3) an
active community \citep{bangerth2013}. Several tools (some specific to Python) are used by
SunPy to make achieving these goals more accessible. To maintain high-quality code, a 
transparent and collaborative development workflow made possible by GitHub is used.
% JI - I don't think we need a description of what is essentially how a project works
% when you use git and github.  There is nothing SunPy specific about this.
The following conditions typically must be met before code is accepted.
\begin{enumerate}
	\item  The code must follow 	
	\href{http://www.python.org/dev/peps/pep-0008/}{PEP8} the Python style 
	guidelines, keeping SunPy code in a consistent.

@@

	\item The code must contain significant unit test coverage.

        \item Community consensus is reached that the new code is valuable.
\end{enumerate}
This kind of development model is widely used within the scientific Python 
community as well as by a wide variety of other projects both open and closed 
source.

Additionally, SunPy makes use of `continuous integration' provided by
\href{http://travis-ci.org}{Travis CI}, a process by which the addition of any new code 
automatically triggers a comprehensive review of written unit tests. If any single test
fails then the community is alerted before the code is accepted. The unit test coverage is
also monitored by the \href{http://coveralls.io}{Coveralls} service.
% JI - what is the coveralls service?

Quality documentation is
one of the most important factors determining the success of any software project. 
Powerful tools already exist in Python to support this, thanks to native
Python's focus on its own documentation. SunPy makes use of the \href{http://sphinx-doc.org}{Sphinx}
documentation generator. Sphinx uses reStructuredText as its markup language: 
an easy-to-read, what-you-see-is-what-you-get plaintext markup syntax. It supports
many output formats most notably HTML as well as PDF, and ePub and provides a rich
hierarchically structured view of in-code documentation strings. The SunPy documentation 
is built automatically and is hosted by \href{http://readthedocs.org}{Read the 
Docs} at \url{http://docs.sunpy.org}.

Communication is the key to maintaining an active community, and so the SunPy community 
uses a number of different tools to facilitate communication. For immediate communications, an active IRC chat
room (\#SunPy) is hosted on freenode.net. For more involved or less immediate needs, such as
developer comments or discussions, a open mailing list is hosted on Google Groups. 
Discussion of bugs and bug tracking are provided directly on GitHub as well as new
code-review discussions.  The SunPy community also reaches out to the wider solar physics
community through presentations, functionality demonstrations and informal meetups at scientific
meetings. 
% RJH: do we want to list both the community and dev lists?

% RJH: This section is redundant with some parts in the text.  I favor cutting the stuff in text.
% schriste - we had agreed to only refer to the support in one place. we need 
%to agree as to where
% SJM: Drop the bits in the code
Many of the larger features in SunPy have been developed 
with the support of both the ESA-SOCIS and GSOC. 
Initial development of SunPy's VSO and HEK 
implementations were funded by the SOCIS program as well as a prototyped GUI 
and N-Dimensional datatype implementations. SunPy was supported by GSOC in 2013 
through the \href{http://www.python.org/psf/}{Python Software Foundation} (PSF). It supported development of the 
\texttt{HELIO} and 
\texttt{database} subpackages.

%JI The section ``Development workflow'' is unnecessary IMHO.  This is
% largely a description of how git and github works.  It is not about sunpy. So I have
% deleted it.
